Towards Verifying the Bitcoin-S Library

### 2022-12-03 final/main.tex
prepare for final oasics submission
Final version

\graphicspath{{./images/}{../images/}}

@@

%\category{} %optional, e.g. invited paper

@@

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% The default bold(bx) is too wide
% Choose a nicer narrower bold
\DeclareFontSeriesDefault[rm]{bf}{b}

@@

\begin{figure}
\lstinputlisting[style=scala]{../code/addition/src/main/scala/extracted/number/NumberType.scala}
  \caption{Extracted Code from NumberType.scala}
  \label{fig:numbertype}
\end{figure}

\begin{figure}
\lstinputlisting[style=scala]{../code/addition/src/main/scala/extracted/currency/CurrencyUnits.scala}
  \caption{Extracted Code from CurrencyUnits.scala}
  \label{fig:currencyunits}
\end{figure}

@@

\begin{figure}
  \lstinputlisting[style=scala, firstline=9, lastline=12,
  firstnumber=9]{../code/addition/src/main/scala/verified/currency/CurrencyUnits.scala}
\caption{Addition function with specification}
\label{fig:spec}
\end{figure}

>>>>

\graphicspath{{./images/}}

@@

\category{Short Paper}

@@

\EventEditors{Bruno Bernardo and Diego Marmsoler}
\EventNoEds{2}
\EventLongTitle{2nd Workshop on Formal Methods for Blockchains (FMBC 2020)}
\EventShortTitle{FMBC 2020}
\EventAcronym{FMBC}
\EventYear{2020}
\EventDate{July 20--21, 2020}
\EventLocation{Los Angeles, California, USA (Virtual Conference)}
\EventLogo{}
\SeriesVolume{84}
\ArticleNo{7}

@@

% The default bold(bx) is too wide
% Choose a nicer narrower bold
%\DeclareFontSeriesDefault[rm]{bf}{b}

@@

\begin{figure}
\lstinputlisting[style=scala]{code/extracted/number/NumberType.scala}
  \caption{Extracted Code from NumberType.scala}
  \label{fig:numbertype}
\end{figure}

\begin{figure}
\lstinputlisting[style=scala]{code/extracted/currency/CurrencyUnits.scala}
  \caption{Extracted Code from CurrencyUnits.scala}
  \label{fig:currencyunits}
\end{figure}

@@

\begin{figure}
  \lstinputlisting[style=scala, firstline=9, lastline=12,
  firstnumber=9]{code/verified/currency/CurrencyUnits.scala}
\caption{Addition function with specification}
\label{fig:spec}
\end{figure}
